Wavelet Spatio-Temporal Change Detection on multi-temporal SAR images

### 2021-12-19 tex/RebutalLetter/RebutalLetter.tex
updates in the rebutal letter

\textcolor{black}{We would like to thank the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards further improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this new submission.}

@@

\textbf{R:} We would like to thank the editor for his comments and for giving us the opportunity to improve the manuscript and submit it again to TGRS. Another coauthor has joined our group and we have been able to improve considerably the manuscript's readability and presentation of our contribution. We hope the editors and reviewers find the current version significantly more appropriate for the journal.
%-------------------------------------

@@

\textbf{R:} We would like to thank the associate editor for his consideration with our manuscript and for allowing us to re-submit our work. The manuscript was carefully reviewed and a thorough analysis was carried out to improve its content. The reviewers' comments have been addressed one by one and below you can find a response to each one of them.
%-------------------------------------

@@

\textbf{R:} We thank the reviewer for all his/her contributions, technical insights, and the time spent on reviewing our manuscript. The manuscript was re-written and the its content was carefully improve.
%-------------------------------------

@@

\textbf{R:} The reviewer is totally right. Even though we wrote PolSAR in the title, the first manuscript did not address the characteristics of this type of image or mentioned related methods from the literature. The term PolSAR was removed from the manuscript and now we let it clear that our method is suitable for single channel images. In the application with real data, we focus on SAR images, what is mentioned in title in the new manuscript.

@@

\textbf{R:} The idea of using correlation screening to detect spatio/temporal changes has not been proposed in the literature yet. Works in feature screening basically employ existing and well known correlation measures, but the application of these techniques in the statistical learning literature is an active research topic regarding high-dimensional data. We show this idea can also offer useful results for satellite image data as well.

@@

\medskip
\textbf{R:} Log-image referred to the logarithm of a matrix representing a image, but such terminology is not longer used in the current manuscript. The epsilon mentioned referred to noise present in an observed image and it did not involve wavelet decomposition. We realized such problems with the presentation of the methodology and re-wrote this section. We hope it is more clear now.

@@

\medskip
\textbf{R:} Presentation of the methodology was carefully revised and now all terms and methods are introduced before being referred to. We present a brief introduction of wavelet decomposition and feature screening that might be enough to understand the following parts of the manuscript. Concerning the approximation level, it is indeed one of the decomposition levels, but we meant that only coefficients related to coarse details are used. This is explained with more details in the current version.
\end{mybox}
%-------------------------------------

@@

\textbf{R:} The four images are now presented separately in Figure 2 of the recent version. The total changes are showed in Figure 3 of this version. The idea is that, if only the first and last images were used (images 1 and 4, respectively), changes in instants between these times would be missed. The proposed method is suited to detect this type of change. Explanations in the section about the simulated images were improved and we added more details on how they were generated.
\end{mybox}
%-------------------------------------

@@

\textbf{R:} Details about the images were included in the text: type of satellite image; type of sensor; resolution; and description of pre-processing steps used before applying the proposed method. We also removed similar figures that were not adding new information to the analysis. The Figures with overlapping curves are no longer used, and different details about the region studied are presented now, including change maps in Figure 6c and Figure 10. In particular, Figure 6c is a validation change map that is used to compute accuracy methods presented in Table 1 of the recent manuscript version.
\end{mybox}
%-------------------------------------

%-------------------------------------
%%%%%%%%%%%%%%%%%%%
\section*{Reviewer \#3}

@@

\medskip
\textbf{R:} The simulated images were indeed generated with additive Gaussian noise. We included more details about how the simulated images were generated and what level of noise was used. The signal to noise to ration considered was chosen in order to not let the true changes too apparent in the observed images (especially image 4), as can be seen in Figure 2. Such level also offers a harder scenario than what is analyzed in the application with real data. Such explanations are presented in the manuscript now.   
\end{mybox}
%-------------------------------------

@@

\medskip
\textbf{R:} Yes, ones (white) correspond to locations were change happened at any instant, whereas zero (black) correspond to places where no change takes place.  This information is given now in the recent version and the figure now is on Figure 3a. We also present more details about the content of other images as well.
\end{mybox}
%-------------------------------------

@@

\medskip
\textbf{R:} We included information about the images used in the real data application. They are indeed Sentinel-1 images.
\end{mybox}
%-------------------------------------

@@

\medskip
\textbf{R:} Yes, each color correspond to a different location (pixel). The goal was to show that locations flagged as change point have squared deviations that behave similarly as the overall measure. Since these Figures were somewhat confusing, we decided not to show them in the recent version.
\end{mybox}
%-------------------------------------

>>>>

\textcolor{black}{We would like to thank you and the reviewers for the valuable comments and the time spent on checking our manuscript. 
We have addressed their comments towards further improving the paper contents and presentation. 
Below we detail the changes and updates incorporated into the manuscript in this new submission.}

@@

\textbf{R:} We would like to thank the editor for his comments and for giving us the opportunity to improve the manuscript and submit it again to TGRS. Another coauthor has joined our group and we have been able to improve the manuscript's readability. We now provide more details in the analyses, show different figure with more informative content and the presentation of our contribution has improved considerably. We hope the editors and reviewers find the current version significantly more appropriate for the journal.
%-------------------------------------

@@

\textbf{R:} We would like to thank the associate editor for his consideration with our manuscript and for allowing us to resubmit our work. The manuscript was carefully reviewed and a thorough analysis was carried out to improve its content. The reviewers' comments have been addressed and below you can find an explanation to each one of them.
%-------------------------------------

@@

\textbf{R:} We thank the reviewer for all his/her contributions, technical insights, and the time spent on reviewing our manuscript. It was re-written and its content was carefully improved.
%-------------------------------------

@@

\textbf{R:} The reviewer is totally right. Even though we wrote PolSAR in the title, the first manuscript did not address the characteristics of this type of image or mentioned related methods from the literature. The term PolSAR was removed from the manuscript and now we let it clear that our method is suitable for single channel images. In the application with real data we focus on SAR images, which is the only type of image mentioned in title now.

@@

\textbf{R:} The idea of using correlation screening to detect spatio/temporal changes has not been proposed in the literature yet. Works in feature screening basically employ existing and well known correlation measures, but the application of these techniques in the statistical learning literature is an active research topic regarding high-dimensional data. We show that this idea can offer useful results for satellite image data analysis as well.

@@

\medskip
\textbf{R:} Log-image referred to the logarithm of a matrix representing an image, but such terminology is no longer used in the current manuscript. The epsilon mentioned referred to noise present in an observed image and it did not involve wavelet decomposition. We realized that such problems were undermining the presentation of our methodology. Therefore, we decided to rewrite this section. We hope it is more clear now.

@@

\medskip
\textbf{R:} Presentation of the methodology was carefully revised and now all terms and methods are introduced before being referred to. We present a brief introduction of wavelet decomposition and feature screening that might be enough to understand further parts of the manuscript. Concerning the approximation level, it is indeed one of the decomposition levels, but we meant that only coefficients related to coarse details are used. This is explained with more details in the current version.
\end{mybox}
%-------------------------------------

@@

\textbf{R:} The four images are now presented separately in Figure 2 of the recent version. The total changes are showed in Figure 3 of this version. The idea is that, if only the first and last images were used (images 1 and 4, respectively), changes in instants between these times would be missed. The proposed method is suited to detect this type of change only observed when considering the full time series of images. Explanations were improved in the section about the simulated images and we added more details on how they were generated.
\end{mybox}
%-------------------------------------

@@

\textbf{R:} Details about the images were included in the text: type of satellite image; type of sensor; resolution; \textcolor{red}{and description of pre-processing steps used before applying the proposed method}. We also removed similar figures that were not adding new information to the analysis. The figures with overlapping curves are no longer used, and different details about the region studied are presented now, including change maps in Figure 6c and Figure 10. In particular, Figure 6c is a validation change map that is used to compute accuracy measure of the methods considered. These measures are given in Table 1 of the recent manuscript version.
\end{mybox}
%-------------------------------------

\newpage
%-------------------------------------
%%%%%%%%%%%%%%%%%%%
\section*{Reviewer \#3}

@@

\medskip
\textbf{R:} The simulated images were indeed generated with additive Gaussian noise. We included more details about how the simulated images were generated and what level of noise was used. The signal to noise to ration considered was chosen in order to not let the true changes too apparent in the observed images (especially image 4), as can be seen in Figure 2. Such level of noise is also more challenging to analyze than what is observed in the application with real data. Such explanations are presented in the manuscript now.   
\end{mybox}
%-------------------------------------

@@

\medskip
\textbf{R:} Yes, ones (white) correspond to locations were change happened at any instant, whereas zeros (black) correspond to places where no change takes place.  This information is given now in the recent version and the figure now is on Figure 3a. We also present more details about the content of the remaining images as well.
\end{mybox}
%-------------------------------------

@@

\medskip
\textbf{R:} We included more detailed information about the images used in the real data application. They are indeed Sentinel-1 images.
\end{mybox}
%-------------------------------------

@@

\medskip
\textbf{R:} Yes, each color corresponds to a different location (pixel). The goal was to show that locations flagged as change point have squared deviations that behave similarly as the overall change measure. Since these figures were somewhat confusing, we decided not to show them in the recent version.
\end{mybox}
%-------------------------------------

### 2021-12-19 tex/paper.wecs/wecs_tgrs.tex
updates in the rebutal letter

Most methods used for change detection analysis can be classified either as supervised (training data is used to set up the method) or unsupervised (fully data-driven techniques). We shall focus in this work on unsupervised approaches, whose examples in the literature include the works of \cite{bruzzone2000automatic,celik2010change,quin2014mimosa,saha2020change,NegriEA2021,NegriFrery2021}. Many other proposals vary in their motivations as well as in their applicability.  Change detection in multi-temporal hyperspectral images is discussed in \cite{bovolo2015time,liu2019review,matsunaga2017current}.  \cite{jia2018novel} pursue change detection techniques via non-local means and principal component analysis. Compressed projection and image fusion are employed by \cite{hou2014unsupervised}. Deep learning by slow feature analysis for change detection is the subject of \cite{du2019unsupervised}. \cite{chen2020change} proposes a change detection method driven by adaptive parameter estimation.

@@

Change detection process using SAR images is a challenging task due to the high-dimensionality of multi-temporal datasets associated with the speckle noise. In this context, the use of Wavelets comes as a convenient approach given robustness when dealing with noise data and the available efficient computational algorithms.

@@

The application of this wavelet transform to $\mathcal{I}^{(m)}$ at some appropriate resolution level $J\geq 1$ results in a matrix of the so called approximation wavelet coefficients $\vX^{(m)}$, a smoothed version of $\mathcal{I}^{(m)}$ 
defined on the same support $\mathcal{S}$. The higher $J\in\{1,2,\ldots, \floor{ \log_2( \min\{u,v\} ) } \}$ is, the smoother $\vX^{(m)}$ gets.

@@

Initially, to express the instantaneous change values with respect to WECS,
Figure~\ref{F:forest_wecs} presents the temporal variations given by $\vd$. According to the presented profile, it is possible to observe the fluctuations around a central value near $12$ as highlight instants with a value similar, higher or lower than this baseline, as pointed out for $m$ equal to 1, 30 and 59, respectively.
%
For the sake of comparison, the wavelet representation at each mentioned instant (i.e., $\vX^{(1)}$, $\vX^{(30)}$ and $\vX^{(59)}$) and the mean image (i.e., $\overline{\mathcal{I}}$) are exhibited in Figure~\ref{F:forest_change_times}. While $\vX^{(1)}$ shares similarities with $\overline{\mathcal{I}}$, evident changes rise in $\vX^{(30)}$. Reversely, $\vX^{(59)}$ offers low contribution for identifying change regions.

>>>>

Most methods used for change detection analysis can be classified either as supervised (training data is used to set up the method) or unsupervised (fully data-driven techniques). We focus in this work on unsupervised approaches, whose examples in the literature include the works of \cite{bruzzone2000automatic,celik2010change,quin2014mimosa,saha2020change,NegriEA2021,NegriFrery2021}. Many other proposals vary in their motivations as well as in their applicability.  Change detection in multi-temporal hyperspectral images is discussed in \cite{bovolo2015time,liu2019review,matsunaga2017current}.  \cite{jia2018novel} pursue change detection techniques via non-local means and principal component analysis. Compressed projection and image fusion are employed by \cite{hou2014unsupervised}. Deep slow feature analysis for change detection is the subject of \cite{du2019unsupervised}. \cite{chen2020change} proposes a change detection method driven by adaptive parameter estimation.

@@

Change detection process using SAR images is a challenging task due to the high-dimensionality of multi-temporal datasets associated with the speckle noise. In this context, the use of Wavelets rises as a convenient approach given robustness when dealing with noise data and the available efficient computational algorithms.

@@

The application of this wavelet transform to $\mathcal{I}^{(m)}$ at some appropriate resolution level $J\geq 1$ results in a matrix of the so called approximation wavelet coefficients $\vX^{(m)}$ of $\mathcal{I}^{(m)}$ 
defined on the same support $\mathcal{S}$. The higher $J\in\{1,2,\ldots, \floor{ \log_2( \min\{u,v\} ) } \}$ is, the smoother $\vX^{(m)}$ gets.

@@

Initially, to express the instantaneous change values with respect to WECS,
Figure~\ref{F:forest_wecs} presents the temporal variations given by $\vd$. According to the presented profile, it is possible to observe the fluctuations around a central value near $12$ as highlight instants with a value similar, higher or lower than this baseline, as pointed out for $m$ equal to 1, 30 and 59, respectively.
%
For the sake of comparison, the wavelet representation at each mentioned instant (i.e., $\vX^{(1)}$, $\vX^{(30)}$ and $\vX^{(59)}$) and the mean image (i.e., $\overline{\mathcal{I}}$) are exhibited in Figure~\ref{F:forest_change_times}. While $\vX^{(1)}$ shares similarities with $\overline{\mathcal{I}}$, evident changes increase in $\vX^{(30)}$. Reversely, $\vX^{(59)}$ offers low contribution for identifying change regions.
